%yright 2007, 2008, 2009 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01

% \documentclass[preprint,11pt]{elsarticle}
\documentclass[final,1p,11pt]{elsarticle}

%\documentclass[final,1p,times]{elsarticle}


%% Use the option review to obtain double line spacing
%%\documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}


\usepackage{epsfig}
%\usepackage{cite}
%\usepackage{mcite}
\usepackage{array,tabularx,epsfig,mathrsfs,graphicx,rotating}
\usepackage{ifthen}
\usepackage{amsfonts}
\usepackage{ragged2e}
\PassOptionsToPackage{hyphens}{url}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{lineno}
\usepackage{subfigure}
\usepackage{epstopdf}
% Custom colors
\usepackage{color}
\usepackage{float}
\usepackage{verbatim}
\usepackage{color,soul}

% to cross text
\usepackage[normalem]{ulem} % either use this (simple) or
\usepackage{soul} % use this (many fancier options)
\usepackage{amsmath,amssymb}

\let\originallesssim\lesssim
\let\originalgtrsim\gtrsim

\DeclareRobustCommand{\lesssim}{%
  \mathrel{\mathpalette\lowersim\originallesssim}%
}
\DeclareRobustCommand{\gtrsim}{%
  \mathrel{\mathpalette\lowersim\originalgtrsim}%
}

\makeatletter
\newcommand{\lowersim}[2]{%
  \sbox\z@{$#1<$}%
  \raisebox{-\dimexpr\height-\ht\z@}{$\m@th#1#2$}%
}
\makeatother


\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue
}




\graphicspath{{figs/}}


\pdfinfo{
   /Author (Chekanov et al)
   /Title  (Studies of granularity of a hadronic calorimeter for tens-of-TeV jets  at a 100 TeV pp collider)
   /CreationDate (D:2017)
   /Subject (PDFLaTeX)
   /Keywords (PDF;LaTeX)
}


\textheight=22cm
\textwidth=14.5cm

\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\la}{\langle}
\newcommand{\promc}{{\sc ProMC}}
\newcommand{\ra}{\rangle}
\newcommand{\eps}{\epsilon}
\newcommand{\ud}{\mathrm{d}}
\newcommand{\Ec}{\mathcal{E}}
\newcommand{\Fc}{\mathcal{F}}
\newcommand{\Za}{\mathrm{Z_1}}
\newcommand{\Zb}{\mathrm{Z_2}}
\newcommand{\Zn}{\mathrm{Z_n}}
\newcommand{\F}{\mathrm{F}}

\chardef\til=126
\newcommand{\GEANTfour} {\textsc{geant4}}
\newcommand{\pythia} {\textsc{Pythia8~}}
\newcommand{\pt}{\ensuremath{p_{\mathrm{T}}}}


\journal{ANL-HEP-149528}

\begin{document}
\hfill ANL-HEP-149528
\definecolor{mygreen}{rgb}{0,0.6,0} \definecolor{mygray}{rgb}{0.5,0.5,0.5} \definecolor{mymauve}{rgb}{0.58,0,0.82}

\lstset{ %
 backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
 basicstyle=\footnotesize,        % the size of the fonts that are used for the code
 breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
 breaklines=true,                 % sets automatic line breaking
 captionpos=b,                    % sets the caption-position to bottom
 commentstyle=\color{mygreen},    % comment style
 deletekeywords={...},            % if you want to delete keywords from the given language
 escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
 extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
 keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
 frame=tb,
 keywordstyle=\color{blue},       % keyword style
 language=Python,                 % the language of the code
 otherkeywords={*,...},            % if you want to add more keywords to the set
 rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
 showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
 showstringspaces=false,          % underline spaces within strings only
 showtabs=false,                  % show tabs within strings adding particular underscores
 stepnumber=2,                    % the step between two line-numbers. If it's 1, each line will be numbered
 stringstyle=\color{mymauve},     % string literal style
 tabsize=2,                        % sets default tabsize to 2 spaces
 title=\lstname,                   % show the filename of files included with \lstinputlisting; also try caption instead of title
 numberstyle=\footnotesize,
 basicstyle=\small,
 basewidth={0.5em,0.5em}
}


\begin{frontmatter}

\title{
Studies of granularity of a hadronic calorimeter for tens-of-TeV jets  at a 100~TeV $pp$ collider 
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\author[add3]{C.-H. Yeh}
\ead{a9510130375@gmail.com}

\author[add1]{S.V.~Chekanov}
\ead{chekanov@anl.gov}

\author[addDuke]{A.V.~Kotwal}
\ead{ashutosh.kotwal@duke.edu}

\author[add1]{J.~Proudfoot}
\ead{proudfoot@anl.gov}

\author[addDuke]{S.~Sen}
\ead{sourav.sen@duke.edu}

\author[add2]{N.V.~Tran}
\ead{ntran@fnal.gov}

\author[add3]{S.-S.~Yu}
\ead{syu@cern.ch}

\address[add3]{
Department of Physics and Center for High Energy and High Field Physics, 
National Central University, Chung-Li, Taoyuan City 32001, Taiwan
}

\address[add1]{
HEP Division, Argonne National Laboratory,
9700 S.~Cass Avenue,
Argonne, IL 60439, USA. 
}

\address[addDuke]{
Department of Physics, Duke University, USA
}

\address[add2]{
Fermi National Accelerator Laboratory
}




\begin{abstract}
Jet substructure variables for hadronic jets with transverse momenta in the range from 2.5~TeV to 20~TeV
were studied using several designs for the spatial size of calorimeter cells. The studies  used 
the full Geant4 simulation 
of calorimeter response combined with realistic reconstruction of calorimeter clusters.
In most cases, the results indicate that the performance of jet-substructure 
reconstruction improves with reducing cell size of a hadronic calorimeter 
from $\Delta \eta \times \Delta \phi = 0.087\times0.087$,
which are similar to the cell sizes of the calorimeters of LHC experiments, by a factor of four, to  $0.022\times0.022$.


\end{abstract}

\begin{keyword}
multi-TeV physics, $pp$ collider, future hadron colliders, FCC, SppC
\end{keyword}



\end{frontmatter}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%, FCC-ee~\cite{Benedikt:2651299}
Particle collisions at energies  beyond those attained at the LHC will lead to many challenges for detector technologies.
Future circular $pp$ colliders~\cite{Mangano:2018mur} such as the European initiatives, FCC-hh~\cite{Benedikt:2018csr}, high-energy LHC (HE-LHC)~\cite{Zimmermann:2018wdi}, and the Chinese initiative, SppC~\cite{Tang:2015qga} will measure high-momentum bosons ($W$, $Z$, $H$) and top quarks with highly-collimated decay products that form jets. 
Jet substructure techniques are used
to identify such boosted particles, and thus can maximize the physics potential of the future colliders.

The reconstruction of jet substructure  variables for collimated jets with transverse momenta above 10 TeV 
requires an appropriate detector design. The most important detector systems for reconstruction of such jets are tracking and calorimetry.
Recently, a number of studies \cite{Calkins:2013ega,Chekanov:2015ihl,Coleman:2017fiq} 
have been discussed using various fast simulation tools, such as 
Delphes  \cite{deFavereau:2013fsa}, in which momenta of particles
are smeared to mimic detector response. 

A major step towards the usage of full Geant4 simulation to verify the granularity requirements 
for calorimeters was made in Ref.~\cite{Chekanov:2016ppq}.
These studies have illustrated a significant impact 
of granularity of electromagnetic (ECAL) and hadronic (HCAL) calorimeters on the
cluster separation between two particles. It was concluded that high granularity is essential 
in resolving two close-by particles for energies above 100 GeV. 

This paper takes the next step in understanding this problem in terms of high-level quantities typically used in physics analyses. Similar to the studies presented in Ref.~\cite{Chekanov:2016ppq}, this paper is based on a full
Geant4 simulation with realistic jet reconstruction.

\section{Simulation of detector response}
\label{sec:sim}

The description of the detector and software used for this study is discussed in Ref.~\cite{Chekanov:2016ppq}.
We use the SiFCC detector geometry with a software package that provides a versatile environment for simulations
of detector performance, testing new technology options, and event reconstruction techniques for future
100~TeV colliders.


The baseline detector discussed in Ref.~\cite{Chekanov:2016ppq}
includes a silicon-tungsten electromagnetic calorimeter with a transverse cell size of 2~$\times$~2~cm$^2$, a steel-scintillator hadronic calorimeter with a transverse cell size of 5~$\times$~5~cm$^2$, and a solenoid outside the ECAL and HCAL that provides a 5 T magnetic field. The studies presented in this paper focus on the performance of  the 
baseline HCAL with the cell size of 5~$\times$~5~cm$^2$, which corresponds to $\Delta \eta \times \Delta \phi = 0.022\times0.022$, where $\eta$ is the pseudorapidity, $\eta \equiv -\ln\tan(\theta/2)$, and $\phi$ is the azimuthal angle.
The depth of the HCAL in the barrel region is 11.25 interaction lengths ($\lambda_I$).
The HCAL has 64 longitudinal layers in the barrel and the endcap regions.

In addition to the baseline HCAL geometry,
two geometry variations were considered without changing other settings. 
We used the HCAL with transverse cell size of
20~$\times$~20~cm$^2$ and  1~$\times$~1~cm$^2$.
In the terms of $\Delta \eta \times \Delta \phi$,  such cell sizes correspond to
$0.087\times0.087$ and  $0.0043\times0.0043$, respectively.

The \GEANTfour\ (version 10.3)~\cite{Allison2016186} simulation of calorimeter response was followed by the full reconstruction of calorimeter clusters formed by the Pandora algorithm~\cite{Charles:2009ta,Marshall:2013bda}. The criteria for clustering in the calorimeter were discussed in Ref.~\cite{THOMSON200925}. We use the same criteria as those in the SiD detector design~\cite{Behnke:2013lya}, which were optimized for a high-granularity HCAL with a cell size of 1~$\times$~1~cm$^2$.
Calorimeter clusters were built from calorimeter hits in the  ECAL and HCAL after applying the corresponding sampling fractions. No other corrections are applied.
Hadronic jets were 
reconstructed with the {\sc FastJet} package~\cite{fastjet} using the anti-$k_T$ algorithm \cite{Cacciari:2008gp}
with  a distance parameter of 0.5. 

In the following discussion, we use the simulations of a heavy $Z'$ boson, 
a hypothetical gauge boson  that arises from extensions of the electroweak symmetry of the Standard Model.
The $Z'$ bosons were simulated with the masses $M=5$, $10$, $20$ and $40$~TeV. The lowest value 
represents a typical mass that is within the reach of the LHC experiments. The  resonance mass of $40$~TeV 
represents the physics reach for a  100~TeV collider. The $Z'$ bosons are forced to decay to two light-flavor quarks ($q\bar{q}$)~\cite{Langacker:2008yv}, $W^+W^-$~\cite{Leike:1998wr} or $t\bar{t}$~\cite{Rosner:1996eb} final states, where the 
$W$ bosons and $t$ quarks decay hadronically. In these scenarios, two highly-boosted
jets are produced,  which are typically back-to-back in the laboratory frame.
The typical transverse momenta of the jets are $\simeq M/2$.
The main difference between the considered decay modes lies in the different jet substructures. In the case of the $q\bar{q}$ decays,
jets do not have any internal structure. In the case of the $W^+W^-$ final state, each jet has two subjets  because of the decay $W\rightarrow q\bar{q}$. In the case of hadronic top decays, jets have three subjets due
to the decay $t \rightarrow  W^+\>b \rightarrow q\bar{q} b$. We use the $Z' \to q\bar{q} \to$~jets process to model the background from QCD jets with approximately the same energy as 
 the $W$ bosons and top quarks.   
The signal events were generated using the \pythia generator~\cite{Sjostrand:2006za} with the default settings,
ignoring interference with SM processes.
The event samples used in this paper are  available from the
HepSim database~\cite{Chekanov:2014fga}.



%%%%%%%%%%%%%% sections 
\input{fcc_jets.tex}

\input{fcc_Mass_soft_drop_for_paper_new_no_UOF_total.tex}

\input{fcc_Mannuwhitney_eff_New_mass_cut_no_UOF_new.tex}

\input{fcc_conclusion.tex}




\section*{Acknowledgements}
This research was performed using resources provided by the Open Science Grid,
which is supported by the National Science Foundation and the U.S. Department of Energy Office of Science. 
We gratefully acknowledge the computing resources provided on Blues, 
a high-performance computing cluster operated by the Laboratory Computing Resource Center at Argonne National Laboratory.
Argonne National Laboratory is supported by the U.S. Department of Energy, Office of Science, Office of High Energy Physics  under contract DE-AC02-06CH11357. The Fermi National Accelerator Laboratory (Fermilab) is operated by Fermi Research Alliance, LLC under Contract No. DE-AC02-07CH11359 with the United States Department of Energy.
This research used resources of the National Energy Research Scientific  Computing Center (NERSC), a U.S. Department of Energy Office of Science  User Facility operated under Contract No. DE-AC02-05CH11231. We gratefully acknowledge Ministry of Science and Technology and Ministry of Education in Taiwan.

\newpage
%%%%%%%%%%%%%%%%%%%%%% references %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{References}

\bibliographystyle{elsarticle-num}
\def\bibname{\Large\bf References}
\def\refname{\Large\bf References}
\pagestyle{plain}
\bibliography{biblio}



\end{document}
